---
title: "Resources for Building Production-Quality Shiny Applications"
format:
  html:
    page-layout: full
    link-external-newwindow: true
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| label: setup
library(pins)
library(reactable)
library(htmltools)
library(dplyr)

# register board for pins package
board <- board_s3(
  bucket = "shinyworkshop-pinboard",
  prefix = "data_dictionary/",
  versioned = TRUE,
  access_key = Sys.getenv("AWS_ACCESS_KEY_ID"),
  secret_access_key = Sys.getenv("AWS_SECRET_ACCESS_KEY_ID"),
  region = Sys.getenv("AWS_REGION")
)

df <- board %>% pin_read("dictionary_list")
df_names <- names(df)

df <- purrr::map2(df, df_names, ~{
  subdf <- mutate(.x, dataset = .y)
  tibble::as_tibble(subdf)
})

df_all <- dplyr::bind_rows(df) %>%
  distinct() %>%
  arrange(dataset, variable)
```


::: callout-warning
This page is under construction and will be updated as the materials are posted online.
:::



## Workshop Data Guide

Throughout this workshop, each of the exercises and live-coding sessions will utilize data from the [Metropolitan Museum of Art](https://www.metmuseum.org), otherwise known as the MET, located in New York, United States. The museum offers data sets associated with the art and objects hosted in the museum via their public [API](https://metmuseum.github.io). Additional metadata associated with each image of the art piece or object was also generated using the [Google Vision API](https://cloud.google.com/vision), and in particular the following methods:

* [Label detection](https://cloud.google.com/vision/docs/labels): Detect and extract information about entities in an image across a broad group of categories.
* [Object annotation](https://cloud.google.com/vision/docs/object-localizer): Detect and extract information about multiple objects in an image.
* [Image properties](https://cloud.google.com/vision/docs/detecting-properties): Detect color attributes of an image.
* [Crop hints](https://cloud.google.com/vision/docs/detecting-crop-hints): Obtain vertices of a cropped region for an image.

```{r}
#| label: art-metadata
#| eval: true
tagList(
  div(
    div(tags$label("Dataset Filter", `for` = "art-type-filter")),
    tags$select(
      id = "art-type-filter",
      onchange = "Reactable.setFilter('art-filter-table', 'dataset', this.value)",
      tags$option("All", value = ""),
      lapply(unique(df_all$dataset), tags$option)
    )
  ),
  
  tags$hr("aria-hidden" = "false"),

  reactable(
    df_all,
    columns = list(
      variable = colDef(
        name = "Variable",
        minWidth = 200,
        cell = function(value, index) {
          type <- df_all$type[index]
          div(
            div(style = list(fontweight = 500), value),
            div(style = list(fontSize = "0.75rem"), type)
          )
        }
      ),
      type = colDef(show = FALSE),
      description = colDef(minWidth = 400),
      dataset = colDef(show = FALSE),
      example = colDef(minWidth = 300)
    ),
    defaultPageSize = 10, 
    elementId = "art-filter-table")
)

```

```{r}
#| label: test
#| eval: false

library(htmltools)

data <- MASS::Cars93[1:15, c("Manufacturer", "Model", "Type", "Price")]

  tagList(
    div(
      div(tags$label("Filter Type", `for` = "cars-type-filter")),
      tags$select(
        id = "cars-type-filter",
        onchange = "Reactable.setFilter('cars-filter-table', 'Type', this.value)",
        tags$option("All", value = ""),
        lapply(unique(data$Type), tags$option)
      )
    ),
    
    tags$hr("aria-hidden" = "false"),

    reactable(data, defaultPageSize = 5, elementId = "cars-filter-table")
  )
```

